### 2010-12-14 resume_cv/cv.tex
Updated my cv a little bit

\section{Publications} \begin{bibsection}
	\item M. Gardner, J. Lutes, J. Lund, J. Hansen, D. Walker, E. Ringger, K.
	  Seppi. The Topic Browser: An Interactive Tool for Browsing Topic Models.
	  To appear in the Challenges of Data Visualization workshop at Neural
	  Information Processing Systems 2010.

	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  In: \emph{Parallel Problem
	  Solving in Nature, 2010}.

	\item Matthew Gardner and Eric Ringger.  Automatic Topic Discovery in 100
	  Years of General Conference Talks.  Presented at the 50th Anniversary
	  BYU Studies Symposium, 2010.

@@

>>>>

\section{Journal Publications}
  \begin{bibsection}
	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  A Speculative
	  Approach to Parallelization in Particle Swarm Optimization.
	  Submitted to: \emph{Swarm Intelligence}.
  \end{bibsection}

\section{Conference Publications}
  \begin{bibsection}
	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  In: \emph{Parallel Problem
	  Solving in Nature, 2010}.

@@

\section{Workshop and other refereed publications}
  \begin{bibsection}
	\item Matthew Gardner, J. Lutes, J. Lund, J. Hansen, D. Walker, E. Ringger,
	  K.  Seppi. The Topic Browser: An Interactive Tool for Browsing Topic
	  Models.  In the Challenges of Data Visualization workshop at \emph{Neural
	  Information Processing Systems, 2010}.

	\item Matthew Gardner and Eric Ringger.  Automatic Topic Discovery in 100
	  Years of General Conference Talks.  Presented at the \emph{50th
	  Anniversary BYU Studies Symposium, 2010}.

  \end{bibsection}
